---
title: "R Notebook"
output: html_notebook
---

# Importing Libraries

```{r}
library(ggplot2)
```

# Loading Data

```{r}
apple_data <- read.csv("AAPL.csv")
```

# Summary

```{r}
summary(apple_data)
```

```{r}
head(apple_data)
```
# Find the structure of the dataset

```{r}
str(apple_data)
```



# Finding Missing Values

```{r}
is.na(apple_data)
```

```{r}
colSums(is.na(apple_data))
```

# Find unique dates in the dataset

```{r}
unique_dates <- unique(apple_data$Date)
print(unique_dates)
```

# Data Visualization

### Convert the Date column to Date type

```{r}
apple_data$Date <- as.Date(apple_data$Date)
```

### Scatter plot of Closing Prices over time, colored by Volume

```{r}
ggplot(apple_data, aes(x = Date, y = Close, color = Volume)) +
  geom_point() +
  labs(title = "Scatter Plot of Closing Prices vs Date Colored by Volume", x = "Date", y = "Closing Price")
```

###  Box plot of Closing Prices

```{r}
ggplot(apple_data, aes(, y = Close)) +
  geom_boxplot(fill = "darkgreen") +
  labs(title = "Box Plot of Closing Prices", x = "", y = "Closing Price")
```

### Histogram of Trading Volume

```{r}
ggplot(apple_data, aes(x = Volume)) +
  geom_histogram( binwidth = 1000000,color = "navy") +
  labs(title = "Histogram of Trading Volume vs Frequency", x = "Volume", y = "Frequency")
```

# Linear Regression Model

### Create a linear regression model to predict Close price based on Open price and summarize the model

```{r}
lm_model <- lm(Close ~ Open, data = apple_data)
summary(lm_model)
```

### Scatter plot with regression line

```{r}
model_visualize = lm(Close ~ Open, data = apple_data)
plot(apple_data$Open, apple_data$Close)
title(main ="Linear Regression: Open vs Close Price")
abline(model_visualize, col = "red")
```

